\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
%
\begin{document}
\mainmatter              % start of the contributions
%
\title{Exact polynomial-time algorithm for the two-machine routing flow shop problem with a restricted transportation network
\thanks{This research was supported by RFBR grant 17-07-00513 and 18-01-00474.} }
%
\titlerunning{Short Title}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Ilya Chernykh\inst{1,2,3} \and
Alexander Kononov\inst{1,2} \and
Sergey Sevastyanov\inst{1,2}} 
%
\authorrunning{Ilya Chernykh, Alexander Kononov and Sergey Sevastyanov } % abbreviated author list (for running head)
%
%
\institute{Sobolev Institute of Mathematics, Novosibirsk, Russia\\
\email{idchern@math.nsc.ru, alvenko@math.nsc.ru, seva@math.nsc.ru}
 \and
Novosibirsk State University, Novosibirsk, Russia\\
Novosibirsk State Technical University, Novosibirsk, Russia \\
 }

\maketitle              % typeset the title of the contribution

\keywords{shop scheduling, routing, dynamic programming}
\\

We consider the routing flow shop problem being a generalization of the flow shop and the metric travelling salesman problems.
The jobs are located at nodes of some transportation network, and the machines travel on the network to execute the jobs in the flow shop environment. 
The machines are initially located at the same node (depot) and must return to the depot after completing all the jobs. 
It is required to find a non- preemptive schedule with the minimal makespan.

The routing flow shop problem was introduced by Averbakh and Berman \cite{AverbakhBerman}. 
It is strongly NP-hard even in the single machine case as it contains the metric TSP as a special case.
Yu et al. \cite{Yu} proved that the two-machine routing flow shop is ordinary NP-hard when the transportation network is a tree
with unbounded number of nodes, i.e. the number of nodes is a linear function on the number of jobs.

In our paper we consider the two-machine routing flow shop under the assumption that a transportation network is an arbitrary undirected graph with a constant number of vertices. 
We present an exact polynomial-time algorithm for this case based on dynamic programming. 
This stands in contrast to the complexity result for the two-machine routing open shop problem
that is NP-hard even on the two-node network \cite{ABC}.






\begin{thebibliography}{1}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }

\bibitem{AverbakhBerman}
Averbakh, I., Berman, O.:  Routing two-machine flow shop problems on networks with special structure. Transportation Science 30, 303--314 (1996).
\bibitem{ABC} 
Averbakh I, Berman O, Chernykh I: The routing open-shop problem on a network: complexity and approximation. European Journal of Operational Research 173(2), 521--39 (2006).
\bibitem{Yu}
Yu W., Liu Z., Wang L., Fan T.: Routing open shop and flow shop scheduling problems. European Journal of Operational Research 213, 24-36 (2011).


\end{thebibliography}
\end{document}
